Model Estimation

### 2018-12-11 model_estimation.Rmd
WIP on estimation notebook

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 2), # distance, size 
  lower = c(-100, 0), # size coefficient must be positive 
  upper = c(0, 100), # distance coefficient must be negative 
  distances = log(distances), parks = parks, tracts = tracts, 
  model = obese_base_sdm, 
  method = "L-BFGS-B", 
  control = list(fnscale = -1, trace = 6))
```

@@

tweets_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 1, 0),
  lower = c(-100, 0, -100), # size coefficient must be positive
  upper = c(0, 100, 100), # distance coefficient must be negative
  hessian=TRUE, distances = distances, parks = parks, tracts = tracts, 
  model = obese_base_sdm, 
  method = "L-BFGS-B", 
  control = list(fnscale = -1, trace = 6))

@@

```{r obesity_access_models}
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = access_sdm_val$par),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = tweets_sdm_val$par),
    # demean
    access_ls = access_ls - mean(access_ls),
    tweets_ls = tweets_ls - mean(tweets_ls)
  )

access_sdm <- update(obese_base_sdm, .~ . + access_ls)
tweets_sdm <- update(obese_base_sdm, .~ . + tweets_ls)
```

@@

# Results
```{r impacts_table}
list("Obesity" = obesity_impacts, "Physical activity" = physact_impacts) %>%
  bind_rows(.id = "Outcome") %>%
  filter(var %in% c("access_ls", "tweets_ls")) %>%
  dplyr::select(-var, -Base)  %>%
  gather("Variable", "Impact", -Outcome, -effect) %>%
  filter(!is.na(Impact))  %>%
  spread(effect, Impact)

>>>>

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-10, 0.001), # distance, size 
  lower = c(-100, 0), # size coefficient must be positive 
  upper = c(0, 100), # distance coefficient must be negative 
  distances = log(distances), parks = parks, tracts = tracts, 
  model = obese_base_sdm, 
  method = "L-BFGS-B", 
  control = list(fnscale = -1, trace = 6))
```

@@

tweets_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(access_sdm_val$par, 0),
  lower = c(-100, 0, -100), # size coefficient must be positive
  upper = c(0, 100, 100), # distance coefficient must be negative
  hessian=TRUE, distances = log(distances), parks = parks, tracts = tracts, 
  model = obese_base_sdm, 
  method = "L-BFGS-B", 
  control = list(fnscale = -1, trace = 6))

@@

```{r show_accessibility}
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = c(-0.8, 0.8)),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = c(-0.8, 0.8, 0.2))
  )

tracts_sf <- tracts_sf %>%
  mutate(
    access_ls = tracts$access_ls,
    tweets_ls = tracts$tweets_ls
  )

pal <- colorQuantile("Spectral", c(tracts_sf$access_ls, tracts_sf$tweets_ls), 5)

leaflet(tracts_sf) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(group = "access", color = ~pal(access_ls)) %>%
  addPolygons(group = "access + tweets", color = ~pal(tweets_ls)) %>%
  addLayersControl(baseGroups = c("access", "access + tweets"))

```{r obesity_access_models}
access_sdm <- update(obese_base_sdm, .~ . + access_ls)
tweets_sdm <- update(obese_base_sdm, .~ . + tweets_ls)
```

@@

# Results
```{r impacts_table}
list("Obesity" = obesity_impacts, "Physical Activity" = physact_impacts) %>%
  bind_rows(.id = "Outcome") %>%
  filter(var %in% c("access_ls", "tweets_ls")) %>%
  dplyr::select(-var, -Base)  %>%
  gather("Measure", "Impact", -Outcome, -effect) %>%
  filter(!is.na(Impact))  %>%
  spread(effect, Impact)
